### 2025-06-02 202507_uai_puncs/neurips2024/content.tex
added uai

@@

@@

\bibliography{references}
\bibliographystyle{iclr2025_conference}

>>>>

\todo{add back this shit at the end for replication and all that super long annoying list of silly questions}

@@

For the interested reader we give the definition of a layered probabilistic circuit in terms of a partition
circuit, as well as a proof that they form valid probability distributions, in Appendix \ref{sec:pc}.

@@

\bibliography{references}
